Share Buyback and Equity Issue Anomalies Revisited

### 2016-02-17 report.Rnw
debugging tool report

#Add any/all choices made in the tool here
if(!exists("input")){
  input = list()
  input$startdate <- as.Date("2000-12-31")
  input$enddate <- as.Date("2014-12-31")
  input$market_cap_min = 50
  input$market_cap_max = 505755
  input$quantile_used_ind = 0.2
  input$quantile_used_all = 0.4

>>>>

#Add any/all choices made in the tool here
if(!exists("input")){
  input = list()
  input$startdate <- as.Date("1984-12-31")
  input$enddate <- as.Date("2014-12-31")
  input$market_cap_min = 250
  input$market_cap_max = 505755
  input$quantile_used_ind = 0.2
  input$quantile_used_all = 0.4
